---
title: "Pick the Lowest Unique Number - Combined Analysis"
author: "Stephen Kaluzny"
date: "December 16, 2015"
output: html_document
---
This is a simple number contest - each person in a group picks a positive integer. The person who selects the smallest value that no else in the group has selected, wins.

The initial idea for the game came from https://plus.maths.org/content/playing-number

This document is a reproducible analysis, see the Appendix for details.

```{r echo=FALSE}
library(ggplot2)
```
## The Data
People in the Seattle TIBCO office were asked via email to send their selected number to me.
A second data set was created by asking 
members of the statsoftful Google group to also participate.

The data for each was entered in a CSV file with Name and Number columns.
Since the data is public on Github,
the respondent's name for the Seattle TIBCO office was replaced by `responderi`,
 where i is the numeric value of the order the entry was received.
The rows in each data set are ordered by the time the email was submitted, older entries first.
The data files are available on github, see the appendix.

Reading the data and combining:
```{r}
seattleofficeDF <- read.csv("seattleoffice.csv", header=TRUE, stringsAsFactors = FALSE)
# seattleofficeDF <- read.csv("seattleoffice_with_names.csv", header=TRUE, stringsAsFactors = FALSE)
statsoftfulDF <- read.csv("statsoftful.csv", header=TRUE, stringsAsFactors = FALSE)
seattlecombinedDF <- rbind(seattleofficeDF, statsoftfulDF)
```
A few individuals submitted numbers to both data sets, we will remove their
entries submitted to the statsoftfulDF:
```{r}
dupPeople <- c("Joe R.", "Walter Y.", "Burl E.")
dupIndx <- match(dupPeople, seattlecombinedDF$Name)
seattlecombinedDF <- seattlecombinedDF[-dupIndx, ]
```

The statsoftful group has 84 members but only `r nrow(statsoftfulDF)` people submitted a number.
The Seattle Office email list has 50 members but only `r nrow(seattleofficeDF)` people submitted a number.

The number of observations in `seattlecombinedDF` is `r nrow(seattlecombinedDF)`.

The data collected over time:

```{r}
plt01 <- ggplot(data=seattlecombinedDF, aes(x=1:nrow(seattlecombinedDF), y=Number))
plt01 + geom_point() + xlab("Time Order")
```

## Analysis
The distribution of the numbers selected:
```{r}
plt02 <- ggplot(data=seattlecombinedDF, aes(x=Number))
plt02 + geom_bar(binwidth=1, fill="blue")
```

The winner:
```{r}
tabNumber <- table(seattlecombinedDF$Number)
if(!any(tabNumber == 1)) {
  cat("No winner since there is no unique number\n")
} else {
  winNumber <- as.numeric(names(tabNumber[tabNumber == 1][1]))
  winName <- seattlecombinedDF$Name[seattlecombinedDF$Number == winNumber]
  cat("Winner: ", winName, "Number:", winNumber, "\n")
}
```
The unique numbers:
```{r}
as.numeric(names(tabNumber[tabNumber == 1]))
```
# Appendix
The source for this document and the data are available on github at:
https://github.com/spkal/LowestUniqueNumber

This is a reproducible analysis, created using R, Rstudio and the knitr package.
To reproduce the analysis, download the R Markdown file,
`LowestUniqueNumberSeattleCombined.Rmd`,
and the data files, `statsoftful.csv` and `seattleoffice.csv`.
from the Github site listed above. Open the R Markdown file in Rstudio
and select the Knit HTML tab at the top of the Markdown file window. 
