---
title: "Pick the Lowest Unique Number - Seattle Office"
author: "Stephen Kaluzny"
date: "December 15, 2015"
output: html_document
---
This is a simple number contest - each person in a group picks a positive integer. The person who selects the smallest value that no else in the group has selected, wins.

The initial idea for the game came from https://plus.maths.org/content/playing-number.

This document is a reproducible analysis, see the Appendix for details.

```{r echo=FALSE}
library(ggplot2)
```
## The Data
People in the Seattle TIBCO office were asked via email to send their selected number to me.

The data was entered in a CSV file with Name and Number columns.
Since the data is public on Github, the respondent's name was replaced by
`responderi`, where i is the numeric value of the order the entry was received.
The rows are ordered by the time the email was submitted, older entries first.
```{r}
seattleofficeDF <- read.csv("seattleoffice.csv", header=TRUE, stringsAsFactors = FALSE)
# seattleofficeDF <- read.csv("seattleoffice_with_names.csv", header=TRUE, stringsAsFactors = FALSE)
```
The Seattle Office email list has 50 members but only `r nrow(seattleofficeDF)` people submitted a number.

The data collected over time:

```{r}
plt01 <- ggplot(data=seattleofficeDF, aes(x=1:nrow(seattleofficeDF), y=Number))
plt01 + geom_point() + xlab("Time Order")
```

## Analysis
The distribution of the numbers selected:
```{r}
plt02 <- ggplot(data=seattleofficeDF, aes(x=Number))
plt02 + geom_bar(binwidth=1, fill="blue")
```

The winner:
```{r}
tabNumber <- table(seattleofficeDF$Number)
if(!any(tabNumber == 1)) {
  cat("No winner since there is no unique number\n")
} else {
  winNumber <- as.numeric(names(tabNumber[tabNumber == 1][1]))
  winName <- seattleofficeDF$Name[seattleofficeDF$Number == winNumber]
  cat("Winner: ", winName, "Number:", winNumber, "\n")
}
```
The unique numbers:
```{r}
as.numeric(names(tabNumber[tabNumber == 1]))
```
# Appendix
The source for this document and the data are available on github at:
https://github.com/spkal/LowestUniqueNumber

This is a reproducible analysis, created using R, Rstudio and the knitr package. To reproduce the analysis, download the R Markdown file, `LowestUniqueNumberStatSoftFul.Rmd`, and the data file, `seattleoffice.csv` from the Github site listed above. Open the R Markdown file in Rstudio and select the Knit HTML tab at the top of the Markdown file window. 
