---
title: "Pick the Lowest Unique Number - StatSoftFul"
author: "Stephen Kaluzny"
date: "December 14, 2015"
output: html_document
---
This is a simple number contest - each person in a group picks a positive integer. The person who selects the smallest value that no else in the group has selected, wins.

The initial idea for the game came from https://plus.maths.org/content/playing-number

This document is a reproducible analysis, see the Appendix for details.

```{r echo=FALSE}
library(ggplot2)
```
## The Data
Members of the statsoftful Google group were asked via email to send their selected number to me.

The data was entered in a CSV file with Name and Number columns.
The rows are ordered by the time the email was submitted, older entries first.
The data is available on github, see the appendix.

```{r}
statsoftfulDF <- read.csv("statsoftful.csv", header=TRUE, stringsAsFactors = FALSE)
```

The group has 84 members but only `r nrow(statsoftfulDF)` people submitted a number.

The data collected over time:

```{r}
plt01 <- ggplot(data=statsoftfulDF, aes(x=1:nrow(statsoftfulDF), y=Number))
plt01 + geom_point() + xlab("Time Order")
```

## Analysis
The distribution of the numbers selected:
```{r}
plt02 <- ggplot(data=statsoftfulDF, aes(x=Number))
plt02 + geom_bar(binwidth=1, fill="blue")
```

The winner:
```{r}
tabNumber <- table(statsoftfulDF$Number)
if(!any(tabNumber == 1)) {
  cat("No winner since there is no unique number\n")
} else {
  winNumber <- as.numeric(names(tabNumber[tabNumber == 1][1]))
  winName <- statsoftfulDF$Name[statsoftfulDF$Number == winNumber]
  cat("Winner: ", winName, "Number:", winNumber, "\n")
}
```
The unique numbers:
```{r}
as.numeric(names(tabNumber[tabNumber == 1]))
```
# Appendix
The source for this document and the data are available on github at:
https://github.com/spkal/LowestUniqueNumber

This is a reproducible analysis, created using R, Rstudio and the knitr package. To reproduce the analysis, download the R Markdown file, LowestUniqueNumberStatSoftFul.Rmd, and the data file, statsoftful.csv, from the Github site listed above. Open the R Markdown file in Rstudio and select the Knit HTML tab at the top of the Markdown file window. 
